Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-12 cvpr2018.tex
15th

\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions. We propose an effective end-to-end trainable single-stream network that can generate photographic high-resolution images (up to $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective multimodal (i.e. image and text) information alignment in order to guarantee semantic consistency and image fidelity simultaneously. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts over all datasets on three different metrics.

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}. However, insufficient methods have been developed to successfully address this task due to its particular challenges. It is a special case of generative learning tasks, which aim to map a low-dimensional embedding to a complex RGB image space. Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions but also fine-grained descriptive details in image pixels.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.48\textwidth]{figure/intro.pdf}
	\vspace{-.4cm}
	\caption{Overview of our method. It contains a single-stream generator and several hierarchically-nested discriminators along the depth dimension of the generator, which are trained end-to-end to generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.4cm}
\end{figure}

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description. But its high-resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical reasons for the challenges of text-to-image synthesis using GANs. The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high-resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution. The contributions are described as follows.

Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel generator convolutional neural network (CNN) framework to cooperate with our nested discriminators more effectively.
To better make use of image and text information in GAN training, 
\textcolor{red}{we enforce nested discriminators at different hierarchies can simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake whole images or image patches.}
This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on its respect duties. 
%It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.95\textwidth]{figure/views2.pdf}
	\vspace{-.2cm}
	\caption{Overviews of some typical GAN frameworks. \textbf{A} decomposes tasks multi-stage GANs \cite{han2017stackgan,denton2015deep}. \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}. \textbf{C} progressively trains symmetric discriminators and generators \cite{Karras2017progressive,huang2016stacked}. \textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.  \textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
\end{figure*}

@@

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

@@

To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from last level of the pyramid, and push up the output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. }
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G)
\end{split}
\end{equation}
where the loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions.

@@

\subsection{Hierarchical-nested adversarial objectives}
%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
Numerous methods have demonstrated a variety of ways to build GANs for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features to learn a stronger generator $\mathcal{G}$. 
The hierarchically-nested objectives 
%We conjecture that adding hierarchical adversarial objective using side outputs can
act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.

@@

%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution. $\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective can be defined as follows: 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
\end{split}
\end{equation}
where $ \mathcal{Y}$ denotes training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies. 
\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images. 
Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than StackGAN \cite{han2017stackgan}. More results can be founded in experiments. 
According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}

\subsection{Functional adaptive adversarial losses}
Our generator produces size-growing side outputs which compose an image pyramid. 
We leverage the hierarchy of it and allow adversarial losses to be multi-purpose to guarantee both semantic consistency and image fidelity.

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and trained to identify two types of errors: real image with mismatch conditional text information and fake image with real text.

@@

To guarantee image fidelity and overcome these two weaknesses, our solution is to add adaptive local adversarial image losses on image patches. The insights are two folds:
\begin{itemize}\vspace{-.1cm}
\setlength\itemsep{-0.3em}
\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details.

@@

\end{itemize}
We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details. Therefore, through the pyramid of the size-growing side outputs, we configure the focal range (the size of each non-overlapping image patch) to be also growing.
The adaptive local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators measure the two losses on the generated images.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{figure/loss.pdf}
	\vspace{-.2cm}
	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches). The focal range increases as image resize grows. Lower range results in finer results. }  \vspace{-.3cm}
	\label{fig:loss}
\end{figure}

@@

Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan} (namely conditional augmentation), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$. We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the $G$ loss to force smooth sampling over the text embedding distribution. }

@@

\section{Experiments}
This section evaluates the proposed method both qualitatively and quantitatively on three public datasets. We denote our method as \textbf{HDGAN}, referring as High-definition results as well as the idea of Hierarchically-nested Discriminators.

\textbf{Dataset} 
\textcolor{red}{We evaluate our method extensively using three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories. We pre-process and split the images following the same pipeline in \cite{reed2016generative,han2017stackgan}
%, which crops the bird region and ensure the foreground occupies greater than 0.75.  
The Oxford-102 dataset \cite{Nilsback08} contains 8189 flow images in 102 different categories. 
%We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
Each image in both datasets is associated with 10 text descriptions. \textcolor{red}{In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.  Each image has 5 text descriptions. }
We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description  into a 1024 embedding vector.
%During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
}

@@

\subsubsection{Style Transfer Using Sentence Interpolation}

>>>>

\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{wrapfig}
\usepackage{makecell}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating images conditioned on semantic image descriptions. We propose an effective end-to-end single-stream network that can generate photographic high-resolution images (up to $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial games inside the network hierarchy, which regularize intermediate representations and assist training to capture the complex image statistics. We present an extensile network architecture to cooperate with discriminators and push generated images to high resolutions. 
We adopt a multi-purpose adversarial learning strategy at multiple nested hierarchical side outputs to encourage more effective image-text alignment in order to guarantee the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images.
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics. 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a translation from a semantic text embedding space to a complex RGB image space. This task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts in descriptions but also fine-grained descriptive details in image pixels. 
However, insufficient methods are developed to successfully address this task due to its particular challenges.

%It is a special case of generative learning tasks, which aim to map a low-dimensional embedding to a complex RGB image space. Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions but also fine-grained descriptive details in image pixels.

\begin{figure}[t]
%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth]{figure/intro.pdf}
	\end{subfigure} \\
\centering
	\begin{subfigure}[t]{0.5\textwidth}
	%	\centering
		\includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
	\end{subfigure}
	\vspace{-.6cm}
	\caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two fine-grained sample results. \label{fig:intro}} 	\vspace{-.3cm}
	%\end{center}
\end{figure}

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%	\vspace{-.3cm}
%	\caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting description. But its high-resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high-resolution and diverse images in an fully end-to-end manner is still an open and attractive question.

We outline several empirical reasons for the challenges of text-to-image synthesis using GANs. The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is stably modeling the huge pixel space in high-resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as guarantee semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these problems, in this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic image (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla-like GAN, without requiring any internal text conditioning like \cite{han2017stackgan} or outside image annotation supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional deep adversarial constraints. 
We introduce accompanying hierarchically-nested objectives at multi-scale intermediate layers to play adversarial games and thereby encourage the generator approaching the real training data distribution. 
We also propose a novel convolutional neural network (CNN) framework for the generator to cooperate with our nested discriminators more effectively.
To guarantee the image diversity and semantic consistency,
\textcolor{red}{we enforce nested discriminators at different hierarchies to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake global images or local image patches with certain focal ranges.}
This multi-purpose conditional adversary is mutually beneficial to allow each focus on its respect duty. 
%% It is a regularization to limit the discriminators to use unexpected information to make decision.

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of the image diversity evaluation metric (inception score \cite{improvedGAN}), we introduce a new visual-semantic similarity measurement to evaluate th alignment between generated images and corresponded text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on three metrics. All source code will be released.

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.95\textwidth]{figure/views2.pdf}
	\vspace{-.2cm}
	\caption{Overviews of some typical GAN frameworks. \textbf{A} uses multi-stage GANs \cite{han2017stackgan,denton2015deep}. \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}. \textbf{C} progressively trains symmetric discriminators and generators \cite{Karras2017progressive,huang2016stacked}. \textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.  \textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
\end{figure*}

@@

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative}  is th first to introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a CNN pretrained on ImageNet \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

@@

To synthesize high-resolution images, cascade networks are useful to decompose original difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and the output from the last pyramid level, and thereby push up the output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage for high-resolution image is unclear. Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs for very high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs progressively, our method has advantages of leveraging multi-level representations to encourage implicit subtask integration, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by these kinds of CNNs with deep supervision. }
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
\end{split}
\end{equation}
\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions. }

@@

\subsection{Hierarchical-nested adversarial objectives}
%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$. 
The hierarchically-nested objectives 
%We conjecture that adding hierarchical adversarial objective using side outputs can
act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.

@@

%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder). $\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
\end{split}
\end{equation}
where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images. 
Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN. More results can be founded in experiments. 
According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}

\subsection{Functional adversarial losses}
Our generator produces size-growing side outputs which compose an image pyramid. 
We leverage the hierarchy of it and allow adversarial losses to be multi-purpose to guarantee both semantic consistency and image fidelity.

To guarantee semantic consistency, we adopt the matching-aware pair loss proposed by \cite{reed2016generative}. The discriminator is designed to take image-text pairs as inputs and is trained to identify two types of fakes: real image with mismatched text and fake image with conditioned text.

@@

To guarantee image fidelity and overcome these two weaknesses, our solution is to add local adversarial image losses on image patches. The insights are two folds:
\begin{itemize}\vspace{-.1cm}
\setlength\itemsep{-0.3em}
\item Further forcing the generated samples to have only only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details.

@@

\end{itemize}
We expect the low-resolution discriminator to focus on global structures, while high-resolution outputs focus more on local image details. Therefore, through the pyramid of the size-growing side outputs, we configure the focal range (the size of each non-overlapping image patch need to classify) to be also growing.
The local image adversarial loss is implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired}.  
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators measure the two losses on the generated images.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.49\textwidth]{figure/loss.pdf}
	\vspace{-.2cm}
	\caption{Given an image in the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and adaptive local image loss (outputting a $R{\times}R$ probability map to indicate real or fake patches). The focal range increases as image resize grows. Lower range results in finer results. }  \vspace{-.3cm}
	\label{fig:loss}
\end{figure}

@@

Furthermore, this separation of the image loss from the matching loss in our method opens further possibilities, such as utilizing the unlabeled image to improve both the generator and discriminator.
\textcolor{red}{In the spirit of variational auto-encoder \cite{vae} and the practice of \cite{han2017stackgan}, namely conditional augmentation (CA), we sample the input text variable $\bm t$ from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are functions of $\bm t$, which produces a $256$-d text input used as the input of the generator.
We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$ \cite{vae}, to the $G$ loss to force the smooth sampling over the text embedding distribution. }

@@

\section{Experiments}
This section evaluates the proposed method both qualitatively and quantitatively on three public datasets. We denote our method as \textbf{HDGAN}, referring as High-Definition results and the idea of Hierarchically-nested Discriminators.

\textbf{Dataset} 
\textcolor{red}{We test on three widely used datasets. The CUB dataset \cite{welinder2010caltech} contains 11,788 bird images belonging to 200 different categories. We pre-process and split the images following the same pipeline in \cite{reed2016generative,han2017stackgan}
%, which crops the bird region and ensure the foreground occupies greater than 0.75.  
The Oxford-102 dataset \cite{Nilsback08} contains 8189 flow images in 102 different categories. 
%We follow \cite{han2017stackgan, reed2016generative} to split both of these datasets into class-disjoint training and testing sets. 
Each image in both datasets is associated with 10 text descriptions. \textcolor{red}{In the COCO dataset, \cite{lin2014microsoft} there are 80k training images and a validation 40k images.  Each image has 5 text descriptions. }
We use the pre-trained text encoder model provided in \cite{reed2016generative} to encode each text description into a 1024 embedding vector.
%During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.
}

@@

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.499\textwidth]{figure/multisample_cub.pdf}
%	\caption{Results on Oxford} \label{fig:multires-cub}
%\end{figure}
